Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-18 article.tex
twist box struc and ref finished.

%!TEX program = xelatex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{float}
\usepackage{physics}

@@

\usepackage{listings}

@@

This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.

\subsection{The Quantum Phase Estimation Algorithm (PEA)}
Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state. Once the state is prepared in our desired state, an approximation is applied to the phase of the operator. The operator $U = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$. Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on in turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state. Next, we measure the phase obtained corresponding to each value of energy. The system as a result collapses to a single state with an associated probability. We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.

\fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{PEA}}
 The molecular energies can be obtained by the time evolution of molecular Hamiltonian. As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$. Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy. In order to preform PEA we need to prepare two parts of qubits. First n qubits of superposition state $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state. Since we can evolve states by unity operator. By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $U$ will transform to each one of qubits in first part.

@@

\end{minipage}}

 \fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{Experimental realisation (SQUID)}}
The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.

@@

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade. In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise. With this extraordinary push of late across Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications, the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.

\section{Technical Boxes}
\section{VQE}
\section{PEA}

\section{Experimental realisation (SQUID)}

>>>>

%!TEX program = xelatex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
%\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{graphicx}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\usepackage{float}
\usepackage{physics}

@@

%\usepackage{listings}

@@

This process is repeated a number of times until the estimate energy approaches a specific value. The final result is an approximation the smallest eigenenergy.\\

\noindent
\fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{VQE}}
In 2014, the VQE algorithm was created by Alberto Peruzzo and Jarrod McClean. VQE comprises of classical and quantum features making it possible to use both classical and quantum resources to determine solutions to problems that are difficult to solve using a classical computer. The flow chart indicates the key instructions of implementing the VQE algorithm. The steps are explained in further detail as follows:

\begin{enumerate}
\item Preparation: Prepare the initial state of the system in terms of the variable theta by applying a quantum circuit. Implementing the unitary coupled cluster (UCC) method enables the algorithm to predict the ground state.
\item Measurement: Measure each local Hamiltonian, $H_{gamma}$  and its corresponding scalar $g_{gamma}$ to find the average value of the Hamiltonian (see Eq. 1 in [article number]).
\item Minimisation: Use a classical tool to find new solutions of theta in order to find the minimum eigenenergy of the Hamiltonian.
\item Repetition: By feeding the settings for theta(vector) into the classical minimisation routine, the new settings for a new parameter of theta(vector) i.e. theta(vector)’. This process is repeated for n iterations until the parameter converges towards to specific value; this will enable an ideal state of the system to be obtained. From this, one can deduce a particular value for $E_{0}$, the smallest energy eigenvalue.
\end{enumerate}
 \end{minipage}}

\subsection{The Quantum Phase Estimation Algorithm (PEA)}
Similarly, to the VQE algorithm, one must ensure that the system is prepared in an initial state, but with the exception that the state must have a sufficient overlap with the ground state. Once the state is prepared in our desired state, an approximation is applied to the phase of the operator. The operator $U = e^{-iHt}$ enables the initial state $\ket{\psi(0)}$ to change over time to the state $e^{-iEt}\ket{\psi(0)}$. Consequently, the initial state is mapped onto a superposition state of various qubits, which is called the ancilla qubits. After that, the state is acted on in turn inducing a phase on the system. Since the way in which the system evolves is controlled, it is now entangled with the initialised state. Next, we measure the phase obtained corresponding to each value of energy. The system as a result collapses to a single state with an associated probability. We repeat this algorithm for a higher number of ancilla qubits \cite[p.2]{tansuwannont2015quantum} until the lowest eigenenergy is obtained, or more precisely the energy of the ground state.\\

\noindent
\fbox{\begin{minipage}[c]{32em}%
 \centerline{\textbf{PEA}}
 The molecular energies can be obtained by the time evolution of molecular Hamiltonian. As any state $\ket{\psi(t)}$ evolved by unitary $U$ can be represent by applying phase difference onto initial state $e^{-iEt}\ket{\psi(0)}$. Phase estimation algorithm (PEA) is used then to find this relative phase and convert it into energy. In order to preform PEA we need to prepare two parts of qubits. First n qubits of superposition state $\frac{\ket{0} + \ket{1}}{\sqrt 2}$, second, our initial state. Since we can evolve states by unity operator. By inputting both parts of qubits onto a multiple controlled-U gate, the eigenvalue of each unitary $U$ will transform to each one of qubits in first part.

@@

\end{minipage}}
\\

\noindent
\fbox{\begin{minipage}[c]{32em}%
\centerline{\textbf{Experimental realisation (SQUID)}}
The physical hardware used for implementing the VQE and PEA algorithms is an Xmon qubit which is a variation of the transmon qubit, a class of superconducting interference device or SQUID. It is a type of charge qubit, which is to say it is a qubit where it’s ‘0’ and ‘1’ basis states are charge states, and the superposition of these charge states is tuned using microwave resonators. The Xmon qubit has a number of favourable features, which include easy fabrication, fast qubit control and long qubit coherence times.

@@

Late last year the US passed the new National Quantum Initiative Act pledging around \textdollar1.2 billion in funding for quantum information science \cite{usbill}. At a similar time the EU commission launched the €1 billion Quantum Technologies Flagship which will fund over 5000 of the top European researchers in quantum technologies over the next decade \cite{eubill}. In the UK, the EPSRC-backed Quantum Technology Hubs represent part of a £270 million investment to create national networks of quantum expertise \cite{ukbill}. With this extraordinary push of late across Europe and also in the US and China, aiming to fast-track quantum technologies out of university research groups and into industrial applications, the importance of this work in quantum chemistry simulations cannot be overstated. As aside from the much touted almost pop-science status of quantum encryption, the myriad opportunities afforded by more efficient scalable quantum chemistry simulations looms large in garnering serious investor interest. The ability to run quantum simulations of the behaviour of molecules and materials is hoped offer new avenues for increasing our understanding of chemistry and enable the development of new medicines and materials in silico.
